Domain-Driven, Generative Data Model for BigPetStore

### 2014-07-19 bdcloud_paper/latex/paper.tex
Added more references

Multiple synethic data set generators exist.  TeraGen \textcolor{red}{cite} and the Intel Hadoop Benchmark Suite \cite{Huang2010} can generate data sets quickly and at any scale. Targetted towards specific benchmarks such as Map-Reduce jobs and Hive queries, the resulting data is semantically-void and not useful for other tasks.  The PGDF (Parallel Data Generation Framework) can quickly generate data and queries that structurally satifies a user-defined relational database schema \cite{Ghazal2013,Rabl2011a,Frank2012,Rabl2011}. The Myriad Toolkit improves on PGDF through a more descriptive model specification language \cite{Alexandrov2012}. Myriad allows the user to specify the distributions for sampling values, simple arithmetic equations for setting the value of fields from other fields, and restrictions on fields domains. Due to the inability to specify underlying dynamic models with latent variables, the data generated by PGDF and Myriad lacks informational complexity and genuine semantics, making it inapprioriate for analytics.

More advanced approaches such as Oligas \cite{Alexandrov2013} and SMOTE \cite{Chawla2002} attempt to generate or extend real data sets with synthetic data sets that satisfy characteristics learned from a real reference data sets. \textcolor{red}{privacy, accuracy without details of underlying process, SMOTE - feature space} Oligos appears promising but will need to overcome several difficult challenges in automatically characterizing complex reference data to determine relevant constraints and learn accurate models that capture the effect of latent variables.

Until such methods have reached maturity, the development of customized, domain-driven models is best suited for satisfying the needs of big data software and algorithms development. For example, the Information Discovery and Analysis System (IDAS) Data Set Generator (IDSG) \cite{Jeske2005,Lin2006} was developed for the Department of Homeland Security to develop synthetic data for effectiveness of IDASs designed to identify potential terrorism threat scenarios.

>>>>

Several synethic data set generators exist.  TeraGen \textcolor{red}{cite} and the Intel Hadoop Benchmark Suite \cite{Huang2010} can generate data sets quickly and at any scale. Targetted towards specific benchmarks such as Map-Reduce jobs and Hive queries, the resulting data is semantically-void and not useful for other tasks.  Multiple frameworks exist for generating synthetic data sets that satisfy relational database schemas \cite{Ghazal2013,Rabl2011a,Frank2012,Rabl2011,Gray1994,Bruno2005}. The more advanced approaches of these allow users to specify relationships between field values through simple arithmetic equations for setting the value of fields from other fields \cite{Alexandrov2012} or use constraint-solving techniques \cite{Arasu2011}. However, due to the inability to specify underlying dynamic models with latent variables, the generated data lacks informational complexity and genuine semantics, making it inapprioriate for analytics.

Recent work is focused on generating synthetic data sets that satisfy characteristics learned from a real reference data sets \cite{Alexandrov2013}. Such approaches appear promising but will need to overcome several difficult challenges in automatically characterizing complex reference data to determine relevant constraints and learn accurate models that capture the effect of latent variables.

Until such methods have reached maturity, the development of customized, domain-driven models is best suited for satisfying the needs of big data software and algorithms development. Several customized, domain-driven models have seen usage in real-world situations.  Information Discovery and Analysis System (IDAS) Data Set Generator (IDSG) \cite{Jeske2005,Lin2006} was developed for the Department of Homeland Security to develop synthetic data for effectiveness of IDASs designed to identify potential terrorism threat scenarios.
